Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2022-02-08 response-to-reviews.Rmd

- **Lines 201-204: $T_{leaf}$ is strongly tied to $T_{air}$, and is further influenced by other micrometeorological drivers (section 1) and by leaf traits and stomatal conductance (see sections 3-4), with leaves adjusting to their environment to approach, when possible, an optimal $T_{leaf}$ for carbon assimilation and metabolic processes (Drake et al., 2020; Perez & Feeley, 2020; Michaletz et al., 2015)**

- **$T_{leaf}$ is strongly tied to $T_{air}$, and is further influenced by other micrometeorological drivers (section 1) and by leaf traits and stomatal conductance (see sections 3-4). Leaves adjust to their environment to approach, when possible, an optimal $T_{leaf}$ for carbon assimilation and metabolic processes **

line52: 'with decreases being more commonly documented across the world’s forests'

**We do not understand this comment, but have verified that this sentence is correct.**

@@

Figure 3: Variables in the inset table need to be stated. I can guess what they are, but this should be explicit.

**We added the description for the variables as part of the figure caption: Variables in the inset table are now described in the figure caption as: "Biohphysical constants in the the table include: shortwave radiation (swr), wind speed (ws), relative humidity (rh), leaf width (lw), stomatal conductance (gs), air temperature (tair)."**

Figure 3: Humid and drought is not a straight comparison. Well-watered vs. drought would be clearer as there are some assumptions about gs in these conditions that underlie the modelling being done here.

**We changed to "humid" to "moist" (as opposed to "well-watered"). We chose the term "moist" because it conveys both high soil moisture and atmospheric humidity, which is what we aim to capture.**

### 2022-02-08 vertical-thermal-review.Rmd
R2 comments

![**Figure `r fig_leaf_T`. Theoretical expectations for variation in the difference between leaf and air temperatures, $T_{Leaf}-T_{air}$, in response to (a) shortwave radiation, (b) wind speed, (c) relative humidity, (d) characteristic leaf width, and (e) stomatal conductance.** Leaf temperatures were modeled using the  *tealeaves* R package of @muir_tealeaves_2019 parameterized to represent a broadleaf species (*Quercus rubra* L.) in a mesic temperate forest (Harvard Forest, Massachusetts, USA) under both humid and dry conditions, as detailed in Supplementary Information Methods `r appendix_tealeaves_methods`. In each scenario, the independent variable was allowed to vary while other parameters were held constant at the values given in the table of biophysical constants. Biohphysical constants in the the table include: shortwave radiation (swr), wind speed (ws), relative humidity (rh), characteristic leaf width (clw), stomatal conductance (gs), air temperature (tair). ](leaf_energy_balance/fig3_leafenergy.png)

>>>>

![**Figure `r fig_leaf_T`. Theoretical expectations for variation in the difference between leaf and air temperatures, $T_{Leaf}-T_{air}$, in response to (a) shortwave radiation, (b) wind speed, (c) relative humidity, (d) characteristic leaf width, and (e) stomatal conductance.** Leaf temperatures were modeled using the  *tealeaves* R package of @muir_tealeaves_2019 parameterized to represent a broadleaf species (*Quercus rubra* L.) in a mesic temperate forest (Harvard Forest, Massachusetts, USA) under both moist and drought conditions, as detailed in Supplementary Information Methods `r appendix_tealeaves_methods`. In each scenario, the independent variable was allowed to vary while other parameters were held constant at the values given in the table of biophysical constants. Biohphysical constants in the the table include: shortwave radiation (swr), wind speed (ws), relative humidity (rh), characteristic leaf width (clw), stomatal conductance (gs), air temperature (tair). ](leaf_energy_balance/fig3_leafenergy.png)
